The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-17 dit-paper_ieee.tex
small reformulation

	\subsection{Model}
		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic
		tasks with constrained deadlines on uniprocessor platforms. Each task
		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period, which is the exact time between two consecutive arrivals.
		The constrained deadline property implies that $D_i \leq T_i \; \forall i$. In
		the following, we differentiate between \emph{synchronous systems} (where $O_i
		= 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).

@@

		The DBF test gives us a list of inequations on the WCET values of the task set
		which together are a necessary and sufficient condition of feasibility. They
		can all be written in the following way:
		\begin{equation}
			\sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
		\end{equation}
		Note that for a given $t$, we have that the $n_i(t)$ are
		constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.

>>>>

	\subsection{Model}
		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic
		tasks with constrained deadlines on uniprocessor platforms. Each task
		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period, which is the exact time between two consecutive arrivals.
		The constrained deadline property implies that $D_i \leq T_i$. In
		the following, we differentiate between \emph{synchronous systems} (where $O_i
		= 0$ for all tasks) and \emph{asynchronous systems} (which are not synchronous).

@@

		The DBF test gives us a list of inequations on the WCET values of the task set
		which, taken together, are a necessary and sufficient condition of feasibility. They
		can all be written in the following way:
		\begin{equation}
			\sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
		\end{equation}
		Note that for given values  of $(t_1, t_2)$, the $n_i(t_1, t_2)$ are
		constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.
